### 2020-05-01 README.Rmd
added unknown fips to NYT

# to retrieve u.s data
all_us <- getus_all()

@@

Data regarding COVID-19 number of cases and deaths (at the county level) were obtained from the [New York Time git repository](https://github.com/nytimes/covid-19-data), whereas number of tests and hospitalizations from the [the Covid Tracking Project](https://covidtracking.com/api}).

>>>>

# to retrieve u.s data you can use 
# the new york times or john hopkins university repository f
all_us <- getus_all(repo = "jhu")

@@

Data regarding COVID-19 number of cases and deaths (at the county level) can be obtained from the [New York Time](https://github.com/nytimes/covid-19-data) or the [Johns Hopkins University](https://github.com/CSSEGISandData), whereas number of tests and hospitalizations from the [the Covid Tracking Project](https://covidtracking.com/api}).
